<!-- ln -s ~/Work/SantiagoCloud/R/CurrencyReader ~/R/x86_64-pc-linux-gnu-library/3.2/shiny/examples/ !-->

---
title: "Currency Reader"
author: "Felipe Santiago"
date: "July 22, 2016"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document was made to explain the R code of the CurrencyReader program that I made.
This is acctually the second part of the program. The Data was already extrated with the Python Service throught Api calls to [CurrencyLayer](https://currencylayer.com/documentation).

<!-- ## The Results -->
<!-- <iframe src="website" style="border: none; width: 440px; height: 900px"></iframe> -->
<!-- ```{r tabsets, echo=FALSE} -->
<!-- shinyAppDir( -->
<!--   system.file("examples/CurrencyReader", package = "shiny"), -->
<!--   options = list( -->
<!--     width = "100%", height = 550 -->
<!--   ) -->
<!-- ) -->
<!-- ``` -->

## The Code Behind
**global.R**
```{r, eval=FALSE}
con <- dbConnect(RMySQL::MySQL(),dbname="?",host="?",port=?,user="?",password="?")

currencyData <- dbGetQuery(con, "select cu.code, 
                           cv.timestamp, 
                           cv.value
                           from currency cu 
                           join currency_value cv on cv.currencyId = cu.id
                           where cu.stopGetValue is NULL and cv.currencyId in(233,254,272,246,261,297)
                           union 
                           select 'USD',  
                           cv.timestamp,
                           1.0
                           from currency_value cv where cv.currencyId = 233
                           order by code")
dbDisconnect(con)
currencyCodes <- unique(currencyData$code)
currencyData <- spread(currencyData, code, value)
currencyData$timestamp <- as.Date(currencyData$timestamp)

```

**server.R**
```{r, eval=FALSE}
library(ggvis)
library(dplyr)

shinyServer(function(input, output, session) {
  
  mutatedCurrencyData <- reactive({ 
    currencyData %>% filter(timestamp >= Sys.Date() - as.numeric(input$displayDays))
  })
  
  yVal <- reactive({
    mutatedCurrencyData()[,input$currencyTo] / mutatedCurrencyData()[,input$currencyFrom]
   })
  
  mutatedCurrencyData %>% 
        ggvis(~timestamp, y = yVal) %>% 
        scale_datetime("x", nice = "day") %>%
        layer_lines(stroke := "DarkGreen") %>%
        add_axis("y", title = "Value To / Value From") %>%
        add_axis("x", title = "Date") %>% 
        bind_shiny("ggvis")
  
  output$table <- renderDataTable(currencyData)
})


```

**ui.R**
```{r, eval=FALSE}
library(ggvis)

fluidPage(fluidPage(
  sidebarPanel(
    selectInput("currencyFrom", "From:", currencyCodes, selected='USD'),
    radioButtons("currencyTo", "To:", currencyCodes, selected='BRL'),
    sliderInput("displayDays", "Display Last (n) Days:", min = 15, max = nrow(currencyData), value = 15)
  ),
  mainPanel(
     ggvisOutput("ggvis")
    ),
  dataTableOutput('table')
))
```